Approximation as Differentiation notes

### 2025-02-09 notes.tex
Fam(I,C) is a functor category where the naturality conditions are trivial because I is discrete.

$\Set$ will often be $\Setoid$ in the Agda code but we'll ignore that here for now.

@@

For $I$ a set and $C$ a category, write $\Fam(I,C)$ for the set of $I$-indexed families of objects of $C$.

Suppose $C$ a category and $I, J$ sets and $x$ an $I$-indexed family of objects of $C$ and $y$ a $J$-indexed
family of objects of $C$. Define $y_f$ for any $f: I \to J$ to be the $I$-indexed family of objects of $C$.

>>>>

\noindent $\Set$ will often be $\Setoid$ in the Agda code but I'm glossing that here.

@@

For any set $I$ and category $C$ write $\Fam(I,C)$ for the category where:
\begin{itemize}
\item the objects are the $I$-indexed families of objects of $C$;
\item a morphism from $X$ to $Y$ is a family of morphisms $f_i: X_i \to Y_i$ in $C$ for any $i \in I$.
\end{itemize}

\noindent Equivalently, $\Fam(I,C)$ is the functor category $\Functors{I}{C}$.

\noindent Suppose $x \in \Fam(I,C)$ and $y \in \Fam(J,C)$. Define $y_f$ for any $f: I \to J$ to be the
$I$-indexed family of objects of $C$.
